---
title: "RTqPCR_20221014"
author: "Liz Hughes"
date: "07/10/2022"
output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE , warning=FALSE, message=FALSE)
```

# Experimental Design

This experiment was set up to examine the expression of Gat201 in different strains grown under the same conditions.

Strains: 
H99, KN99-alpha (KNa), Madhani-Gat201 deletion mutant (M-Gat201) and 2 Gat201 complemented strains (into Madhani-Gat201 deletion strain) C26 and C30.

Culture conditions:
Set up overnight cultures from a single colony in YPD at 30 degrees, 150rpm, 2 biological replicates.
Cultures were set up in 20 ml RPMI at an OD of 0.1 from the ON culture. Cell were washed with RPMI prior to testing the OD and setting up cultures in RPMI. Cultures were incubated at 37 degrees, 150rpm for 7 hours.

Sample collection: 
19 ml Samples were collected at 6 hours. Samples were fixed in methanol on dry ice for 3-5 mins. My Cryptococcus RNA extraction protocol was followed to isolate RNA from samples.The samples were NOT lyophilise due to timr constraints.

Replicates:
3 biological replicates were collected for each sample.
3 technical replicates +RT and 1 -RT

Test Primers:
Gat201 CNAG_01551 (set 1)
Gat201 CNAG_06762 (Set 1)
Liv 3 CNAG_05835 (Set 1)


Reference gene primers: 
CNAG_04994 (SRP14)
CNAG_00483 (ACT1)
CNAG_00121 (GDP1)





```{r load_packages}
library(tidyverse)
library(cowplot)
library(tidyqpcr)
library(dplyr)
library(rlang)
library(markdown)
library(ggplot2)
theme_set(theme_bw())
```

# Create Plateplan 4 hours
## list target_ids of primer sets

```{r target_ids_4}

colkey <- create_colkey_6_in_24(target_id = c("Gat201", "Gat204", "Liv3", "SRP14", "ACT1", "GDP1"))

print(colkey)
```

## Set up experimental samples
```{r samples_4}
Samples <- c("H99-1", "H99-2", "H99-3", "KN99alpha-1", "KN99alpha-2", "KN99alpha-3", "deltaGat201-1", "deltaGat201-2", "deltaGat201-3", "C26-1", "C26-2", "C26-3", "C30-1", "C30-2", "C30-3")

TechReps <- c("1", "2", "3")

rowkey <- tibble(well_row=LETTERS[1:15], 
                 sample_id= Samples)

print(rowkey)
```


## Plateplan
```{r plate_plan}

plate <- label_plate_rowcol(
  plate = create_blank_plate(well_row = LETTERS[1:15], well_col = 1:24),
  rowkey = rowkey,
  colkey = colkey
)

print(plate)
display_plate(plate)

```




# Load data for plate

```{r plate}
plate <- read_tsv( "~/Edward Wallace/Lab based work/ComplementedCloneChecks/20221014_ComplementCheck_EH_Ct.txt",  
                    skip=1) %>%
    mutate(well=Pos,cq=Cp) %>%
    right_join(plate)

plate
```


# Split Sample column into BioRep, Time, Condition

```{r separate conditions}
plate_sep <- separate(plate, 
         sample_id, 
         into = c("Sample" , "BioRep"), 
         sep = "-", 
         remove = FALSE)
view(plate_sep)
```



```{r plate_sep}

ggplot(data = plate_sep) +
  geom_point(aes(x = target_id, y = cq, shape = prep_type, colour = target_id),
    position = position_jitter(width = 0.2, height = 0)
  ) +
  labs(
    y = "Quantification cycle (Cq)",
    title = "All reps, unnormalized"
  ) +
  facet_wrap(~sample_id) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```


```{r plate_sep_refgenes}

  ggplot(data = filter(plate_sep, target_id == c("SRP14", "ACT1", "GDP1") )) +
  geom_point(aes(x = target_id, y = cq, shape = prep_type, colour = target_id),
    position = position_jitter(width = 0.2, height = 0)
  ) +
  labs(
    y = "Quantification cycle (Cq)",
    title = "All reps, unnormalized"
  ) +
  facet_grid(~sample_id) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```




```{r}
plate_norm <- plate_sep %>%
  group_by(sample_id)%>%
  filter(prep_type == "+RT" )%>%
  calculate_deltacq_bysampleid(ref_target_ids = c("SRP14", "ACT1", "GDP1"))

plate_norm

```

# Plot delta Cq for normalized data

```{r Plate_norm_plot_Cq}

ggplot(data = filter(plate_norm, target_id != c("SRP14", "ACT1", "GDP1") )) +
  geom_point(aes(x = target_id, y = delta_cq, colour = sample_id),
    position = position_jitter(width = 0.2, height = 0)
  ) +
  labs(y = "delta Cq") +
  
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))


```


```{r save_jpeg}


ggsave("~/Edward Wallace/Lab based work/ComplementedCloneChecks/ComplementCloneCheck.png", 
 ,width = 10,height=7)
```



```{r Plate_norm_plot_Cq}

ggplot(data = filter(plate_norm, target_id == c("Gat201") )) +
  geom_point(aes(x = target_id, y = delta_cq, colour = sample_id),
    position = position_jitter(width = 0.2, height = 0)
  ) +
  labs(y = "delta Cq") +
  facet_wrap(~sample_id) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))


```


```{r Plate_norm_plot_Cq}

ggplot(data = filter(plate_norm, target_id == c("Gat201") )) +
  geom_point(aes(x = target_id, y = delta_cq, colour = sample_id),
    position = position_jitter(width = 0.2, height = 0)
  ) +
  labs(y = "delta Cq") +
  facet_grid(~sample_id) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))


```






